DataCleaning

### 2014-07-24 DataManipulation/DataManipulation.Rmd
Recreated the proof of concept with hour 19 and checked the other trends ideas.

library(sqldf)

@@

>>>>

#need to kill a few columns with . in the name
Forecasts$Evaluated.at.<-NULL
Forecasts$Effective.<-NULL
names(Forecasts)[1:24]<-c("F01","F02","F03","F04","F05","F06","F07","F08","F09","F10","F11","F12","F13","F14","F15","F16","F17","F18","F19","F20","F21","F22","F23","F24")
Forecasts$Date<-Forecasts$ForecastDate

library(plyr)
RTO<-join(Forecasts, Loads, by="Date")

#clean up
rm(Forecasts,Loads)

#
JustTrends$TrendDate<-JustTrends$Date
JustTrends$Date<-as.POSIXct(JustTrends$Date)+2*60*24*60

WTrends<-join(RTO,JustTrends, by="Date")
#save for later use
save(WTrends,file="WTrends")

@@

Summary
```{r}
summary(WTrends)
